Rotation Periods in Low-Mass Binary Stars: The Impact of Tidal Torques

### 2018-11-13 Paper/sync.tex
Updates from ShareLaTeX

@@

@@

In both the CPL and CTL model, We assume $k_2 = 0.5$. This choice of $k_2$ does not impact our results as $k_2$ is degenerate with Q in the CPL model, e.g. the $k_2/Q$ scaling in Eq.~(\ref{eqn:cpl:z}), and with $\tau$ in the CTL model, e.g. $k_2 \tau$ scaling in Eq.~(\ref{eqn:ctl:z}), so we instead examine how our results scale with $Q$ and $\tau$.

@@

\begin{figure}
	\includegraphics[width=\textwidth]{../Plots/lockedCPL.pdf}
   \caption{Caption.}%
    \label{fig:lockedCPL}%
\end{figure}

@@

\begin{figure}
	\includegraphics[width=\textwidth]{../Plots/lockedCTL.pdf}
   \caption{Caption.}%
    \label{fig:lockedCTL}%
\end{figure}

>>>>

- we use Lurie+2017 Prots that "Assuming solar-like differential rotation, P1,min will be closest to the equatorial rotation period. This provides a consistent reference point for the differential rotation discussion below."

@@

talk about how most people have focused on circularization, sync is hard to measure, we focus on low-mass stars with convective envelopes where the eqtide model is applicable, not higher mass stars with radiative envelopes where dynamical tide effects likely dominate (e.g. stuff lurie talked about)

@@

In both the CPL and CTL model, We assume $k_2 = 0.5$. This choice of $k_2$ does not impact our results as $k_2$ is degenerate with Q in the CPL model, e.g. the $k_2/Q$ scaling in Eq.~(\ref{eqn:cpl:z}), and with $\tau$ in the CTL model, e.g. $k_2 \tau$ scaling in Eq.~(\ref{eqn:ctl:z}), so we instead examine how our results scale with $Q$ and $\tau$.  Any constraints we derive for $Q$ and $\tau$ can trivially be scaled to other values of $k_2$.

@@

\begin{figure}
	\includegraphics[width=0.45\textwidth]{../Plots/lockedCPL.pdf}
   \caption{Caption.}%
    \label{fig:lockedCPL}%
\end{figure}

@@

\begin{figure}
	\includegraphics[width=0.45\textwidth]{../Plots/lockedCTL.pdf}
   \caption{Caption.}%
    \label{fig:lockedCTL}%
\end{figure}
